Open source landscape ecology tools

### 2020-07-21 paper/paper.Rmd
stars with spatial data download

<!-- mention different data types/formats/projections/extents/resolutions -->
<!-- access to spatial data -->
<!-- rgee -->

@@

## Spatial regression
<!-- MH: Do we really want to include this? Not really a landscape ecology topic but rather (geo) spatial stats I would argue -->

>>>>

Nowadays, spatial data for many spatial scales is available from abundance of sources.
Some of them require registration or having appropriate credentials and allows downloading only from the web interface.
However, many of the sources made their data publicly available either as a direct download or through an API connection.
This is used by some R packages allowing for downloading various environmental spatial dataset.

<!-- elevatr + ?? - elevation -->
<!-- land cover -->
<!-- rgbif + ?? -->
<!-- rgee -->

@@

## Spatial regression
<!-- MH: Do we really want to include this? Not really a landscape ecology topic but rather (geo) spatial stats I would argue -->
<!-- JN: we could wait with this section to after receiving the results of the questionnaire -->
